Manuscript for Foodborne-Outbreak Project

### 2023-04-23 code/analysis_code/statistical_analysis.qmd
update
final RMSEs

test_data_final %>% select(Illnesses) %>% 
  bind_cols(placeholder_illnesses) %>% rmse(Illnesses, .pred)

@@

test_data_final %>% select(Hospitalizations) %>% 
  bind_cols(placeholder_hosp) %>% rmse(Hospitalizations, .pred)

@@

```{r}
# Illness
# Univariate

# Multivariate
save_location <- here("results","tables", "illness_rmse_models.rds")
saveRDS(illness_model_dataframe, file = save_location)

# Hospitalizations
save_location <- here("results", "tables","hospital_rmse_models.rds")
saveRDS(hosp_model_dataframe, file = save_location)
```

>>>>

final_illness_fit <- test_data_final %>% select(Illnesses) %>% 
  bind_cols(placeholder_illnesses) %>% rmse(Illnesses, .pred)

@@

final_hosp_fit <- test_data_final %>% 
  select(Hospitalizations) %>% 
  bind_cols(placeholder_hosp) %>% rmse(Hospitalizations, .pred)
```

@@

```{r}
# Illness
save_location <- here("results","tables", "illness_rmse_models.rds")
saveRDS(illness_model_dataframe, file = save_location)

save_location <- here("results", "tables", "final_illness_fit.rds")
saveRDS(final_illness_fit, file = save_location)

# Hospitalizations
save_location <- here("results", "tables","hospital_rmse_models.rds")
saveRDS(hosp_model_dataframe, file = save_location)

save_location <- here("results", "tables", "final_hosp_fit.rds")
saveRDS(final_hosp_fit, file = save_location)
```

### 2023-04-23 products/manuscript/Manuscript2.qmd
final RMSEs

# Final model metrics

```

@@

Fitting the finalized random forest model to the test data resulted in RMSEs of 36.6 and 6.70 for the health outcomes of illnesses and hospitalizations, respectively.

>>>>

# Final model metrics
data_location <- here("results", "tables", "final_illness_fit.rds")
final_illness_fit <- readRDS(data_location)

data_location <- here("results", "tables", "final_hosp_fit.rds")
final_hosp_fit <- readRDS(data_location)
```

@@

Fitting the finalized random forest model to the test data resulted in RMSEs of `r final_illness_fit$.estimate[1]` and `r final_hosp_fit$.estimate[1]` for the health outcomes of illnesses and hospitalizations, respectively.
